---
title: 'Case Study 11: Interacting with space'
author: "Etienne Beaulac"
date: "3/26/2018"
output: 
  html_document:
    keep_md: true
---
```{r backgroud, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
library(leaflet)
library(USAboundaries)
library(buildings)
library(tidyverse)
library(geofacet)
library(sf)
library(sp)
library(geojsonio)
library(maps)

states <- st_as_sf(map("state", fill = TRUE, plot = FALSE))
map.dat <- us_states()
counties <- as(us_counties(),"Spatial")


all.permits <- permits %>%
  filter(variable == "All Permits")

single.family <- permits %>%
  filter(variable == "Single Family", year > 2005) %>% 
  mutate(name = gsub(pattern = " County", replacement = "",x = countyname))

all.multi <- permits %>%
  filter(variable == "All Multifamily")

single.family.sum <- single.family %>% 
  group_by(StateAbbr, year) %>% 
  summarize(value = sum(value)) %>% 
  ungroup() %>% 
  filter(year > 2005)

all.permits.sum <- all.permits %>% # summarize sum by state
  group_by(StateAbbr, year) %>% 
  summarize(value = sum(value)) %>% 
  rename(value_all = value) %>% 
  inner_join(single.family.sum, by = c("StateAbbr", "year"))

states <- geojson_read("us-states.geojson", what = "sp")
class(states)

single.family.sum <- single.family.sum %>%
  left_join(map.dat %>% select(name, state_abbr), by = c("StateAbbr" = "state_abbr")) %>% 
  select(name, StateAbbr, value, year)

newobj <- sp::merge(states, single.family.sum, by = "name", duplicateGeoms = TRUE)
countiesobj <- sp::merge(counties, single.family, by = "name", duplicateGeoms = TRUE)
sp.point.df <- split(newobj, newobj$year)
counties.df <- split(countiesobj, countiesobj$year)
```
## Maps, time-series, crashes
Here is the Leaflet that I created to display the mortage crisis in the United States. 

* You can select between state-view and county-view
* You can select a year from 2006-2010
* You can click on a state and see its name
* You can click on a county and see its name and state
* Yellow is low, red is high

As you can see, in most states the mortgage crisis had a strong effect on the number of permits given. However, it seems that it was already slowing down even before the actual crisis, so it might indicate that there were some signs of the crisis even before the known crisis years.

```{r leaflet, echo=TRUE, message=FALSE, warning=FALSE, eval=TRUE}
m <- leaflet() %>%
  setView(-96, 37.8, 4) %>%
  addTiles()

bins <- c(100, 500, 1000, 2000, 5000, 10000, 20000, 100000, 200000, Inf)

names(sp.point.df) %>%
  purrr::walk( function(df) {
    pal <- colorBin("YlOrRd", domain = sp.point.df[[df]]$value, bins = bins)
    
    m <<- m %>%
      addPolygons(data = sp.point.df[[df]],
                  group = paste(df, "States", sep = " - "),
                  fillColor = ~pal(value),
                  weight = 2,
                  opacity = 1,
                  color = "White",
                  dashArray = "3",
                  fillOpacity = 0.7,
                  popup = sp.point.df[[df]]$name
                  ) 
  })

bins <- c(0, 10, 50, 100, 500, 1000, 5000, 10000, 50000, Inf)

names(counties.df) %>%
  purrr::walk( function(df) {
    pal <- colorBin("YlOrRd", domain = counties.df[[df]]$value, bins = bins)

    m <<- m %>%
      addPolygons(data = counties.df[[df]],
                  # label = ~as.character(value),
                  group = paste(df, "Counties", sep = " - "),
                  fillColor = ~pal(value),
                  weight = 0.7,
                  opacity = 0.7,
                  color = "white",
                  dashArray = "3",
                  fillOpacity = 0.7,
                  popup = paste(counties.df[[df]]$state_name, paste(counties.df[[df]]$name, "County", sep = " "), sep = " - ")
                  )
  })

m %>% 
  addLayersControl(baseGroups = c(paste(names(sp.point.df), "Counties", sep = " - "), paste(names(sp.point.df), "States", sep = " - ")),
                   options = layersControlOptions(collapsed = FALSE)) 
```

