---
title: "Case Study 1"
author: "Etienne Beaulac"
date: "1/13/2018"
output:  
  html_document:  
    keep_md: true  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## "The Decline of Mass Incarceration is Good for Everyone"
#### <https://www.washingtonpost.com/news/wonk/wp/2018/01/11/the-decline-of-mass-incarceration-is-good-for-everyone/>

This is an interesting data visualization because it is so simple, and maybe too simple. It is intented to show that mass incarceration is decreasing, but that is only half of what the title of the article is saying! It should also aim to show that mass incarceration had negative impacts on society, which Joseph Smith, while running for President of the United States, had said and insisted upon. 

However, there are also some things about the graph that don't really work out. First, the colors don't match up. The lines and the titles are not the same color! Also, more traditional colors could've been used, such as blue for males and pink for females. Is it sexist? Maybe, but it subconsciously makes it easier to register the differences. 


## Showing employment/unemployment
#### <https://projects.fivethirtyeight.com/jobs-report-growth-unemployment/>

I really liked this visualization because it showed how different types of visualizations can show different aspects of a problem such as unemployment. It starts off by showing the typical bar graph that is very straightforward but lacks information. 

At the end of the article, a compilation of graphs are put forth, showing all of the detail that the bar graph was unable to accurately represent, such as whether or not the unemployed people actually wanted a job.


## When Does Work Actually Get Done?
#### <https://priceonomics.com/when-does-work-actually-get-done/>

This article had quite a few graphs that all portrayed their own important pieces of information. One was about the time when the most work go done, another about the day, the date, and the season. These all kept the same color scheme: mostly red, except for the first one that also had blue to show created work. This feature was left out in the other graph probably because it was shown as closely related to the completed work. 

I think it was very clever that they put the percentages on the bars of the bar graphs to make it easier to read and understand. It gets clear that the beginning of the year seems less productive because more goals are being set than are being met, whereas at the end of the year, stuff needs to get done.


## The Comic Sans Index: What Kind of Fonts Do Americans Use?
#### <https://priceonomics.com/the-comic-sans-index-what-kind-of-fonts-do/>

This analysis of data is very important to me: who likes Comic Sans anyways? Well, through the nicely made bubble maps I was able to understand this aspect of the strange world better. Basically, people in Texas are avid users of strange fonts. There were 5 charts that were split into the different characteristics of fonts, such as sans serif or with serif. 

I think the colors that were used were meant to corelate with the category, but it was a little too much for my taste. Aside from that, it didn't really take away from the information that was presented. A bubble map visualization was the perfect tool to use to show this data.

```{r echo=FALSE}
plot(1:20)
```

